% compensation.tex
% Compensation structure: Revenue splits based on initial insurance claim amounts
% Trial Period: 70/30 split | Post-Trial: 50/50 split
% Company retains 100% of supplement revenue

\section{Compensation Structure}
\label{sec:compensation}

\subsection{Revenue Sharing Basis}
\label{subsec:revenue-basis}

This Agreement establishes a revenue-sharing arrangement based on \textbf{initial insurance
claim amounts only}. The Specialist shall receive a percentage of payments received from
insurance carriers for initial claims processed by the Specialist. The Company shall separately
prepare and negotiate insurance supplements and shall retain one hundred percent (100\%) of
all supplement revenue.

\subsubsection{Definition: Initial Insurance Claim Amount}
For purposes of this Agreement, the \defterm{Initial Insurance Claim Amount} means the total
amount paid by an insurance carrier for the initial claim approval, before any supplements
are submitted, and excluding:
\begin{itemize}
    \item Sales tax or other taxes;
    \item Any insurance supplement amounts (which are separately handled by the Company);
    \item Amounts designated by the insurance carrier for general overhead and profit
          that were part of any previous estimate not related to the current claim;
    \item Any amounts collected that are later refunded or charged back by the insurance carrier.
\end{itemize}

The Initial Insurance Claim Amount represents the insurance carrier's payment for the damage
assessment, materials, labor, and related costs approved in the initial claim filed and
processed by the Specialist.

\subsection{Trial Period Revenue Split (First 8 Jobs)}
\label{subsec:trial-split}

For the first eight (8) Completed Jobs as defined in Section~\ref{sec:trial-period}, the
revenue from Initial Insurance Claim Amounts shall be divided as follows:

\begin{enumerate}
    \item \textbf{Specialist Compensation:} The Specialist shall receive \percentage{70}
          (seventy percent) of the Initial Insurance Claim Amount.

    \item \textbf{Company Compensation:} The Company shall receive \percentage{30}
          (thirty percent) of the Initial Insurance Claim Amount.
\end{enumerate}

This 70/30 revenue split applies only to Initial Insurance Claim Amounts. The Company retains
100\% of any insurance supplement revenue during the Trial Period.

\subsection{Post-Trial Revenue Split (Job 9 Onward)}
\label{subsec:post-trial-split}

Beginning with the ninth (9th) Completed Job and continuing for all subsequent jobs during
the term of this Agreement, the revenue from Initial Insurance Claim Amounts shall be divided
equally:

\begin{enumerate}
    \item \textbf{Specialist Compensation:} The Specialist shall receive \percentage{50}
          (fifty percent) of the Initial Insurance Claim Amount.

    \item \textbf{Company Compensation:} The Company shall receive \percentage{50}
          (fifty percent) of the Initial Insurance Claim Amount.
\end{enumerate}

This 50/50 equal revenue split applies only to Initial Insurance Claim Amounts. The Company
retains 100\% of any insurance supplement revenue after the Trial Period.

\subsection{Supplement Revenue}
\label{subsec:supplement-revenue}

\subsubsection{Company Responsibility for Supplements}
The Company shall be solely responsible for preparing, documenting, and negotiating any
insurance supplement claims that arise from jobs where the Specialist has processed the
initial insurance claim.

\subsubsection{Company Retains All Supplement Revenue}
The Company shall retain one hundred percent (100\%) of all amounts collected from insurance
carriers for supplement claims. The Specialist shall have no claim, right, or entitlement
to any portion of supplement revenue, regardless of the supplement amount or the job count.

\subsubsection{Supplement Definition}
Insurance supplements are additional claims submitted to the insurance carrier after the
initial claim has been approved and paid, typically when additional damage is discovered
during the roofing work or when the initial claim estimate missed items or damage that
should have been covered.

\subsection{Payment Terms}
\label{subsec:payment-terms}

\subsubsection{Payment Timing}
The Company shall pay the Specialist their share of any Initial Insurance Claim Amount within
\textbf{fifteen (15) business days} following the Company's receipt of payment from the
insurance carrier for the initial claim.

\subsubsection{Payment Method}
Unless otherwise agreed in writing, all payments shall be made by:
\begin{itemize}
    \item Check mailed to the Specialist's address listed in Section~\ref{sec:parties}; or
    \item Electronic transfer (ACH or wire transfer) to the Specialist's designated bank account; or
    \item Such other method as mutually agreed upon in writing by the Parties.
\end{itemize}

\subsubsection{Payment Documentation}
With each payment, the Company shall provide the Specialist with documentation including:
\begin{itemize}
    \item The customer name and property address;
    \item The insurance carrier and claim number;
    \item The Initial Insurance Claim Amount received from the insurance carrier;
    \item The calculation of the Specialist's share (70\% or 50\% depending on job count);
    \item The date payment was received from the insurance carrier;
    \item The job number in the sequence of Completed Jobs.
\end{itemize}

\subsection{Compensation Summary}
\label{subsec:compensation-summary}

For clarity, the compensation structure throughout the term of this Agreement is summarized
as follows:

\vspace{8pt}

\begin{center}
\begin{tabular}{|l|c|c|c|}
\hline
\textbf{Job Range} & \textbf{Specialist Share} & \textbf{Company Share} & \textbf{Supplement Revenue} \\
\hline
Jobs 1--8 (Trial)  & 70\% of initial claim & 30\% of initial claim & 100\% Company \\
\hline
Job 9+ (Post-Trial) & 50\% of initial claim & 50\% of initial claim & 100\% Company \\
\hline
\end{tabular}
\end{center}

\vspace{8pt}

\textit{Note: The revenue splits shown above apply exclusively to Initial Insurance Claim
Amounts as defined in Section~\ref{subsec:revenue-basis}. Insurance supplement revenue is
not shared and is retained entirely by the Company as described in Section~\ref{subsec:supplement-revenue}.}
