% general-provisions.tex
% Standard legal boilerplate provisions

\section{General Provisions}
\label{sec:general}

\subsection{Entire Agreement}
\label{subsec:entire-agreement}

This Agreement, including all exhibits and attachments hereto, constitutes the entire
agreement between the Parties with respect to the subject matter hereof and supersedes
all prior and contemporaneous agreements, understandings, negotiations, and discussions,
whether oral or written, between the Parties.

No representation, promise, inducement, or statement of intention has been made by either
Party that is not embodied in this Agreement, and neither Party shall be bound by or
liable for any alleged representation, promise, inducement, or statement of intention
not so set forth.

\subsection{Amendments and Modifications}
\label{subsec:amendments}

No amendment, modification, or waiver of any provision of this Agreement shall be effective
unless it is in writing and signed by both Parties. Any such written amendment shall
expressly reference this Agreement and the specific provisions being amended.

Oral modifications or amendments shall not be enforceable. Course of dealing or course
of performance shall not modify the terms of this Agreement.

\subsection{Governing Law}
\label{subsec:governing-law}

This Agreement shall be governed by and construed in accordance with the laws of the
State of Oklahoma, without giving effect to any choice of law or conflicts of law
principles that would cause the application of the laws of any other jurisdiction.

\subsection{Severability}
\label{subsec:severability}

If any provision of this Agreement is held to be invalid, illegal, or unenforceable by
a court of competent jurisdiction, such provision shall be deemed modified to the minimum
extent necessary to make it valid and enforceable. If such modification is not possible,
the provision shall be severed from this Agreement.

The invalidity, illegality, or unenforceability of any provision shall not affect the
validity, legality, or enforceability of any other provision of this Agreement, and the
remaining provisions shall continue in full force and effect.

If any provision is severed, the Parties shall negotiate in good faith to replace the
severed provision with a valid and enforceable provision that achieves, to the greatest
extent possible, the original intent and economic effect of the severed provision.

\subsection{Waiver}
\label{subsec:waiver}

\subsubsection{No Implied Waiver}
No failure or delay by either Party in exercising any right, power, or remedy under this
Agreement shall operate as a waiver thereof, nor shall any single or partial exercise of
any right, power, or remedy preclude any other or further exercise thereof or the exercise
of any other right, power, or remedy.

\subsubsection{Written Waiver Required}
No waiver shall be effective unless it is in writing and signed by the Party against whom
the waiver is sought to be enforced. Any such waiver shall be limited to the specific
instance and shall not be deemed a waiver of any subsequent breach or default.

\subsubsection{No Waiver by Conduct}
The waiver by either Party of a breach of any provision of this Agreement shall not operate
or be construed as a waiver of any subsequent breach of the same or any other provision.

\subsection{Assignment}
\label{subsec:assignment}

\subsubsection{Restriction on Assignment}
Neither Party may assign, transfer, or delegate any of its rights or obligations under
this Agreement without the prior written consent of the other Party, which consent shall
not be unreasonably withheld, conditioned, or delayed.

\subsubsection{Permitted Assignments}
Notwithstanding the foregoing, either Party may assign this Agreement without consent:
\begin{itemize}
    \item To an affiliate, subsidiary, or parent company, provided that the assignor remains
          liable for all obligations under this Agreement;
    \item In connection with a merger, consolidation, or sale of all or substantially all
          of the assignor's assets or business to which this Agreement relates;
    \item To a successor entity resulting from a corporate reorganization.
\end{itemize}

\subsubsection{Effect of Assignment}
Any attempted assignment in violation of this Section shall be void and of no effect.
Subject to the restrictions above, this Agreement shall be binding upon and inure to the
benefit of the Parties and their respective successors and permitted assigns.

\subsection{Notices}
\label{subsec:notices}

\subsubsection{Notice Requirements}
All notices, requests, demands, and other communications required or permitted under this
Agreement shall be in writing and shall be deemed to have been duly given:

\begin{enumerate}
    \item On the date of delivery if delivered personally;
    \item On the date of transmission if sent by email (with confirmation of receipt);
    \item One (1) business day after deposit with a nationally recognized overnight courier;
    \item Three (3) business days after deposit in the United States mail, postage prepaid,
          certified or registered mail, return receipt requested.
\end{enumerate}

\subsubsection{Notice Addresses}
Notices shall be sent to the Parties at the following addresses (or such other address
as a Party may designate by notice to the other Party):

\vspace{8pt}

\textbf{To Company:}

\begin{tabular}{@{}l}
    Heavenly Roofing LLC \\
    3313 Elmo Way \\
    Moore, Oklahoma 73160 \\
    Email: \placeholder{FILL IN COMPANY EMAIL}
\end{tabular}

\vspace{12pt}

\textbf{To Specialist:}

\begin{tabular}{@{}l}
    \placeholder{FILL IN SPECIALIST NAME} \\
    \placeholder{FILL IN ADDRESS LINE 1} \\
    \placeholder{FILL IN CITY, STATE ZIP} \\
    Email: \placeholder{FILL IN SPECIALIST EMAIL}
\end{tabular}

\subsection{Counterparts and Electronic Signatures}
\label{subsec:counterparts}

\subsubsection{Execution in Counterparts}
This Agreement may be executed in one or more counterparts, each of which shall be deemed
an original, but all of which together shall constitute one and the same instrument.

\subsubsection{Electronic Signatures}
The Parties agree that electronic signatures, digital signatures, and electronically
transmitted signatures (including PDF signatures) shall have the same legal effect and
enforceability as original handwritten signatures.

\subsubsection{Electronic Delivery}
This Agreement may be delivered by email, electronic transmission, or other electronic
means, and such delivery shall be deemed effective delivery for all purposes.

\subsection{Force Majeure}
\label{subsec:force-majeure}

Neither Party shall be liable for any failure or delay in performing its obligations
under this Agreement (except payment obligations) to the extent such failure or delay
is caused by events beyond the Party's reasonable control, including but not limited to:

\begin{itemize}
    \item Acts of God (earthquakes, floods, storms, fires, etc.);
    \item War, terrorism, civil unrest, or riot;
    \item Government actions, laws, or regulations;
    \item Epidemic, pandemic, or quarantine restrictions;
    \item Labor disputes or strikes;
    \item Failure of utilities or communication systems;
    \item Material shortages or transportation disruptions.
\end{itemize}

The Party affected by a force majeure event shall promptly notify the other Party and
shall use commercially reasonable efforts to resume performance as soon as practicable.

\subsection{Headings}
\label{subsec:headings}

The section and subsection headings in this Agreement are for convenience only and shall
not affect the interpretation or construction of this Agreement.

\subsection{Interpretation}
\label{subsec:interpretation}

\begin{itemize}
    \item Unless the context clearly requires otherwise, the singular includes the plural
          and vice versa;
    \item References to ``including'' or ``includes'' shall mean ``including without limitation'';
    \item The words ``herein,'' ``hereof,'' and ``hereunder'' refer to this Agreement as a whole;
    \item References to Sections refer to sections of this Agreement unless otherwise specified;
    \item Each Party has participated in the negotiation and drafting of this Agreement,
          and any rule of construction that ambiguities are to be resolved against the
          drafting party shall not apply.
\end{itemize}

\subsection{Survival}
\label{subsec:survival}

The following provisions shall survive the expiration or termination of this Agreement:

\begin{itemize}
    \item Section~\ref{sec:confidentiality} (Confidentiality and Non-Disclosure)
    \item Section~\ref{sec:liability} (Liability and Indemnification)
    \item Section~\ref{sec:dispute} (Dispute Resolution)
    \item Section~\ref{subsec:termination-effect} (Effect of Termination)
    \item This Section~\ref{subsec:survival} (Survival)
    \item Any provisions relating to payment of earned compensation
    \item Any other provisions that by their nature are intended to survive
\end{itemize}

\subsection{Further Assurances}
\label{subsec:further-assurances}

Each Party agrees to execute and deliver such additional documents and instruments and
to take such further actions as may be reasonably necessary or desirable to carry out
the provisions of this Agreement and to consummate the transactions contemplated hereby.

\subsection{Relationship of Parties}
\label{subsec:relationship}

This Agreement does not create any partnership, joint venture, agency, franchise, sales
representative, or employment relationship between the Parties. Neither Party has any
authority to bind the other Party or to incur any obligation on behalf of the other
Party without the prior written consent of such Party.

\subsection{Publicity}
\label{subsec:publicity}

Neither Party shall issue any press release or make any public announcement regarding
this Agreement or the relationship between the Parties without the prior written consent
of the other Party, except as required by law or regulation.

Each Party may, however, list the other Party as a client or business partner in marketing
materials and on its website, subject to the other Party's right to request removal of
such reference.
