% sample-filled-contract.tex
% Example contract with filled placeholder values
% This demonstrates what the final contract looks like with all fields completed

\documentclass[12pt,letterpaper]{article}

% Load custom style package (note the ../ to go up one directory)
\usepackage{../styles/contract-style}

% Override placeholder command to show filled values in normal text (not red)
\renewcommand{\placeholder}[1]{#1}

% Override company and specialist information with sample data
\renewcommand{\specialistname}{John Michael Smith}
\renewcommand{\specialistaddress}{1234 Oak Street, Oklahoma City, Oklahoma 73101}

\title{Independent Contractor Agreement - Sample}
\author{Heavenly Roofing LLC}
\date{\today}

\begin{document}

\thispagestyle{firstpage}

% ============================================================================
% TITLE AND FRONT MATTER
% ============================================================================

\contracttitle{Independent Contractor Agreement}
\contractsubtitle{Insurance Supplement Specialist Services}

\begin{center}
    \textbf{Effective Date:} March 1, 2026
\end{center}
\vspace{18pt}

% ============================================================================
% SECTION 1: PARTIES (FILLED VERSION)
% ============================================================================

\section{Parties to the Agreement}
\label{sec:parties}

This Independent Contractor Agreement (the \defterm{Agreement}) is entered into
as of the Effective Date by and between:

\vspace{12pt}

\textbf{COMPANY:}

\begin{tabular}{@{}ll}
    \textbf{Name:}    & Heavenly Roofing LLC \\
    \textbf{Address:} & 3313 Elmo Way \\
                      & Moore, Oklahoma 73160 \\
    \textbf{Entity Type:} & Oklahoma Limited Liability Company \\
\end{tabular}

\vspace{12pt}

Hereinafter referred to as the \defterm{Company} or \defterm{Heavenly Roofing}.

\vspace{18pt}

\textbf{SPECIALIST:}

\begin{tabular}{@{}ll}
    \textbf{Name:}    & John Michael Smith \\
    \textbf{Address:} & 1234 Oak Street \\
                      & Oklahoma City, Oklahoma 73101 \\
    \textbf{Entity Type:} & Individual / Sole Proprietor \\
\end{tabular}

\vspace{12pt}

Hereinafter referred to as the \defterm{Specialist}.

\vspace{12pt}

The Company and the Specialist are collectively referred to as the \defterm{Parties}
and individually as a \defterm{Party}.

% ============================================================================
% REMAINING SECTIONS (USE SAME FILES)
% ============================================================================

\input{../sections/recitals}

% Term and Scope section (inline since it's in main contract.tex)
\section{Term and Scope of Services}
\label{sec:term}

\subsection{Engagement}
This Agreement shall commence on the Effective Date and shall continue until
terminated by either party in accordance with Section~\ref{sec:termination} of this Agreement.

\subsection{Services}
The Specialist shall provide the following services to the Company:

\begin{enumerate}
    \item Review and analyze insurance claims related to roofing damage;
    \item Prepare and negotiate insurance supplement claims to maximize recovery;
    \item Communicate with insurance adjusters and carriers on behalf of the Company;
    \item Document and photograph property damage to support supplement claims;
    \item Provide expertise and guidance on insurance claim procedures and best practices;
    \item Such other related services as may be mutually agreed upon by the parties.
\end{enumerate}

\subsection{Independent Contractor Relationship}
The parties expressly agree that the Specialist is an independent contractor and not
an employee, agent, partner, or joint venturer of the Company. The Specialist shall
have no authority to bind the Company or incur any obligation on behalf of the Company
without the Company's prior written consent.

\input{../sections/compensation}
\input{../sections/trial-period}
\input{../sections/knowledge-exchange}
\input{../sections/termination}
\input{../sections/confidentiality}
\input{../sections/liability}
\input{../sections/dispute-resolution}

% General provisions with filled email addresses
\section{General Provisions}
\label{sec:general}

\subsection{Entire Agreement}
\label{subsec:entire-agreement}

This Agreement, including all exhibits and attachments hereto, constitutes the entire
agreement between the Parties with respect to the subject matter hereof and supersedes
all prior and contemporaneous agreements, understandings, negotiations, and discussions,
whether oral or written, between the Parties.

No representation, promise, inducement, or statement of intention has been made by either
Party that is not embodied in this Agreement, and neither Party shall be bound by or
liable for any alleged representation, promise, inducement, or statement of intention
not so set forth.

\subsection{Amendments and Modifications}
\label{subsec:amendments}

No amendment, modification, or waiver of any provision of this Agreement shall be effective
unless it is in writing and signed by both Parties.

\subsection{Governing Law}
\label{subsec:governing-law}

This Agreement shall be governed by and construed in accordance with the laws of the
State of Oklahoma.

\subsection{Severability}
\label{subsec:severability}

If any provision of this Agreement is held to be invalid, illegal, or unenforceable,
the remaining provisions shall continue in full force and effect.

\subsection{Waiver}
\label{subsec:waiver}

No failure or delay by either Party in exercising any right shall operate as a waiver thereof.

\subsection{Assignment}
\label{subsec:assignment}

Neither Party may assign this Agreement without the prior written consent of the other Party.

\subsection{Notices}
\label{subsec:notices}

All notices shall be in writing and sent to:

\vspace{8pt}

\textbf{To Company:}

\begin{tabular}{@{}l}
    Heavenly Roofing LLC \\
    3313 Elmo Way \\
    Moore, Oklahoma 73160 \\
    Email: contact@heavenlyroofingokc.com
\end{tabular}

\vspace{12pt}

\textbf{To Specialist:}

\begin{tabular}{@{}l}
    John Michael Smith \\
    1234 Oak Street \\
    Oklahoma City, Oklahoma 73101 \\
    Email: john.smith@example.com
\end{tabular}

\subsection{Counterparts and Electronic Signatures}
\label{subsec:counterparts}

This Agreement may be executed in counterparts and electronic signatures are valid.

% Signatures (simplified for sample)
\newpage

\section*{Execution of Agreement}

\textbf{IN WITNESS WHEREOF}, the Parties have executed this Independent Contractor
Agreement as of the Effective Date.

\vspace{0.5in}

\noindent\textbf{HEAVENLY ROOFING LLC}

\vspace{0.5in}

\noindent\textit{[Signature would appear here]}

\vspace{0.3in}

\noindent Sarah Johnson, Managing Member

\vspace{0.6in}

\noindent\textbf{INSURANCE SUPPLEMENT SPECIALIST}

\vspace{0.5in}

\noindent\textit{[Signature would appear here]}

\vspace{0.3in}

\noindent John Michael Smith

\vspace{0.4in}

\begin{center}
\textit{Note: This is a sample contract for demonstration purposes only.}\\
\textit{Actual contracts must be reviewed by legal counsel before execution.}
\end{center}

\end{document}
